Neuroecon Poster Figures

### 2017-10-04 code/NeuroeconPoster.Rmd
added new version of condensed plots and poster

@@

@@

ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 35, height = 56, units = "in", limitsize = FALSE)
```

@@

>>>>

p3nl <- arrangeGrob(p1 +theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1)

@@

ggsave('Lit_Review_Poster_Plot_nl.jpg', plot = p3nl, device = "jpeg", path = "../output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)

@@

ggsave('Bootstrap_Poster_Plot.jpg', plot = p6, device = "jpeg", path = "../output/figures/", width = 24, height = 42, units = "in", limitsize = FALSE)
```

@@

Summarizing at task level

```{r}
p1_t <- fig_data_poster %>%
  filter(task == 'task') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  theme_bw()+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 50))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p2_t <- fig_data_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(y = factor(task_group, levels=rev(unique(task_group))), x = retest_reliability)) + 
  geom_point(aes(size=sample_size, shape = type), color='#F8766D')+
  theme_bw()+
  theme(axis.text.y = element_text(size=43),
        legend.position = 'none') + 
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_y_discrete(labels = function(x) str_wrap(x, width = 10))+
  scale_shape_manual(breaks = sort(fig_data$type), values = c(15, 16, 17, 3))+
  scale_size_continuous(range = c(5, 50))+
  geom_vline(xintercept = 0, color = "red", size = 1)

p3_t <- arrangeGrob(p1_t, p2_t, nrow=1)

ggsave('Lit_Review_Poster_Plot_t.jpg', plot = p3_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)
```

```{r}
p4_t <- boot_df_poster %>%
  filter(task == 'task') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#00BFC4')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p5_t <- boot_df_poster %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p6_t <- arrangeGrob(p4_t, p5_t,nrow=1)

ggsave('Bootstrap_Poster_Plot_t.jpg', plot = p6_t, device = "jpeg", path = "../output/figures/", width = 26, height = 45, units = "in", limitsize = FALSE)

```{r warning=FALSE, message=FALSE}
p10 = measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  select(-var, -task) %>%
  left_join(rel_df[,c("dv", "icc")], by="dv")%>%
  # filter(ddm_task == 1) %>%
  separate(variable_type, c("overall_difference", "raw_EZ_hddm", "param"), extra="merge") %>%
  mutate(raw_EZ_hddm = ifelse(ddm_task == 0, "other", raw_EZ_hddm),
         param = ifelse(ddm_task == 0, "other", param)) %>%
  na.omit() %>%
  ggplot(aes(icc))+
  geom_histogram(aes(fill=param),  alpha=0.5, position = 'identity')+
  facet_grid(.~factor(raw_EZ_hddm, levels = c("raw", "EZ", "hddm", "other"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion", "Other")))+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30),
        strip.text = element_text(size=30))+
  guides(fill  = guide_legend(nrow = 1))

ggsave('Measure_type_comp_Poster.jpg', plot = p10, device = "jpeg", path = "../output/figures/", width = 30, height = 6, units = "in")
```
